---
title: "Yukon Chinook salmon run-reconstructions and reference points"
date: "2023-02-22"
output:
  html_document:
    collapsed: no
    fig_caption: yes
    highlight: espresso
    number_sections: yes
    smooth_scroll: yes
    theme: sandstone
    toc: yes
    toc_float: yes
    keep_md: true
---
```{=html}
<style type="text/css">

body{ /* Normal  */
      font-size: 15px;
  }
td {  /* Table  */
  font-size: 14px;
}
h1.title {
  font-size: 24px;
  color: Black;
}
h1 { /* Header 1 */
  font-size: 19px;
  color: Black;
}
h2 { /* Header 2 */
    font-size: 16px;
  color: Black;
}
</style>
```
This document summarizes run-reconstructions for lower, middle, and upper (Canadian) Yukon River Chinook salmon (*Oncorhynchus tshawytscha*) stock aggregates as well as biological reference points for the Canadian stock. These estimates are based on a integrated state-space run reconstruction and spawner-recruitment model fit to data (1981-2022) from various assessment projects that estimate mainstem passage, harvests, tributary escapements, stock-proportions, and age-composition, under a single Bayesian estimation framework. 

Full model details and sensitivity analyses are described in: 

>Connors, B.M., Bradley C.A., Cunningham C., Hamazaki T., and Liller, Z.W. 2022. Estimates of biological reference points for the Canadian-origin Yukon River mainstem Chinook salmon (*Oncorhynchus tshawytscha*) stock aggregate. DFO Can. Sci. Advis. Sec. Res. Doc. 2022/031.iv + 100 p.

Repository with all data and code to reproduce data updates, model fitting, and this doc, can be found [here](https://github.com/Pacific-salmon-assess/yukon-imeg-model). 
```{r setup, include=FALSE}
# Settings and libraries
knitr::opts_chunk$set(echo = FALSE, message=FALSE, cache=FALSE, warning=FALSE, include=TRUE)
knitr::opts_chunk$set(dpi=300)
options(scipen=1, digits=4)

library(tidyverse)
library(dplyr)
library(ggthemes)
library(rstan)
library(rstantools)
library(here)
library(beepr)
library(BEST)
library(tidybayes)
library(kableExtra)
library(ggthemes)
library(mcmcplots)
library(bayesplot)
library(reshape2)
library(ggpubr)
library(viridis)
library(gsl)

# Read in Model Data and Output Files for each of the three models (base/body count, total eggs and total egg mass versions)
stan.fit.bodies <- readRDS(here("03_outputs","base.stan.fit.2022.rds"))
stan.data.bodies <- readRDS(here("03_outputs","base.stan.data.2022.rds"))
model_bodies_pars <- rstan::extract(stan.fit.bodies)

# Benchmarks
max_samples <- dim(model_bodies_pars$lnalpha_c)

sr_years <- stan.data.bodies$years
nyrs <- length(sr_years)

benchmarks <- summary(stan.fit.bodies, pars= c( "lnalpha_c","beta", "sigma_R", "phi", "S_max", "S_eq_c", "Smsy_Sch_corr","Umsy_Sch_corr"))$summary[,c(1,4,6,8:10)]

rownames(benchmarks) <- c("log (alpha)", "beta", "sigma R", "phi", "Smax", "Seq", "Smsy", "Umsy")

benchmarks <- benchmarks[,c(1,3,2,4:6)]

```

# Figures

## Run-reconstructions

```{r fig1, echo=FALSE, fig.align = "center", fig.dim = c(8, 6)}
# summarize run estimates
canrun <- model_bodies_pars$can_run
canrun.quant <- t(apply(canrun, 2, quantile, probs=c(0.025,0.5,0.975)))/1000
midrun <- model_bodies_pars$mid_run
midrun.quant <- t(apply(midrun, 2, quantile, probs=c(0.025,0.5,0.975)))/1000
lowrun <- model_bodies_pars$low_run
lowrun.quant <- t(apply(lowrun, 2, quantile, probs=c(0.025,0.5,0.975)))/1000
totrun <- canrun + midrun + lowrun
totrun.quant <- t(apply(totrun, 2, quantile, probs=c(0.025,0.5,0.975)))/1000

#summarize esc estimates
canesc <- model_bodies_pars$canesc
canesc.quant <- t(apply(canesc, 2, quantile, probs=c(0.025,0.5,0.975)))/1000
midesc <- model_bodies_pars$midesc
midesc.quant <-t(apply(midesc, 2, quantile, probs=c(0.025,0.5,0.975)))/1000
lowesc <- model_bodies_pars$lowesc
lowesc.quant <- t(apply(lowesc, 2, quantile, probs=c(0.025,0.5,0.975)))/1000
totesc <- canesc + midesc + lowesc
totesc.quant <- t(apply(totesc, 2, quantile, probs=c(0.025,0.5,0.975)))/1000

#rm(canrun, midrun, lowrun, totrun, canesc, midesc, lowesc, totesc)

#median(totrun); median(canrun);median(midrun); median(lowrun)
#max(totrun.quant[,2]); min(totrun.quant[,2])
#run_cor <- cor(cbind(canrun.quant[,2],midrun.quant[,2],lowrun.quant[,2]))
#median(run_cor[row(run_cor)!=col(run_cor)])

#dataframe
counts.sum <- rbind(canrun.quant, midrun.quant, lowrun.quant, totrun.quant, canesc.quant,
                    midesc.quant, lowesc.quant, totesc.quant)
colnames(counts.sum) <- c("low95", "med50", "hi95")
counts.fig <- data.frame(year = rep(sr_years,8), 
                         stock = rep(c("Canada", "Middle", "Lower", "Total"), 
                                  each = nyrs), 
                         count = rep(c("Run", "Escapement"), 
                                  each = nyrs*4), 
                         counts.sum, stringsAsFactors = TRUE)

#summarize harvest estimates
canhar <- model_bodies_pars$can_run - model_bodies_pars$canesc
canhar.quant <- t(apply(canhar, 2, quantile, probs=c(0.025,0.5,0.975)))
midhar <- model_bodies_pars$mid_run - model_bodies_pars$midesc
midhar.quant <-t(apply(midhar, 2, quantile, probs=c(0.025,0.5,0.975)))
lowhar <- model_bodies_pars$low_run - model_bodies_pars$lowesc
lowhar.quant <- t(apply(lowhar, 2, quantile, probs=c(0.025,0.5,0.975)))
tothar <- canhar + midhar + lowhar
tothar.quant <- t(apply(tothar, 2, quantile, probs=c(0.025,0.5,0.975)))

#summarize harvest rate estimates
canharrate <- ((model_bodies_pars$can_run - model_bodies_pars$canesc)/model_bodies_pars$can_run)*100
canharrate.quant <- t(apply(canharrate, 2, quantile, probs=c(0.025,0.5,0.975)))
midharrate <- ((model_bodies_pars$mid_run - model_bodies_pars$midesc)/model_bodies_pars$mid_run)*100
midharrate.quant <-t(apply(midharrate, 2, quantile, probs=c(0.025,0.5,0.975)))
lowharrate <- ((model_bodies_pars$low_run - model_bodies_pars$lowesc)/model_bodies_pars$low_run)*100
lowharrate.quant <- t(apply(lowharrate, 2, quantile, probs=c(0.025,0.5,0.975)))
totharrate <- ((canhar + midhar + lowhar)/(canrun + midrun + lowrun))*100
totharrate.quant <- t(apply(totharrate, 2, quantile, probs=c(0.025,0.5,0.975)))

#rm(canhar, midhar, lowhar, tothar, canharrate, midharrate, lowharrate, totharrate)

#max(canharrate.quant[,2]); min(canharrate.quant[,2]); median(canharrate.quant[,2])
#max(midharrate.quant[,2]); min(midharrate.quant[,2]); median(midharrate.quant[,2])
#max(lowharrate.quant[,2]); min(lowharrate.quant[,2]); median(lowharrate.quant[,2])

#dataframe
counts.sum <- rbind(canhar.quant, midhar.quant, lowhar.quant, tothar.quant, canharrate.quant,
                    midharrate.quant, lowharrate.quant, totharrate.quant)
colnames(counts.sum) <- c("low95", "med50", "hi95")
harvest.fig <- data.frame(year = rep(sr_years,8), 
                         stock = rep(c("Canada", "Middle", "Lower", "Total"), 
                                  each = nyrs), 
                         count = rep(c("Harvest", "Harvest rate"), 
                                  each = nyrs*4), 
                         counts.sum, stringsAsFactors = TRUE)


harvest.fig$stock <- factor(harvest.fig$stock, levels = c("Canada", "Middle", "Lower", "Total"))


b <- ggplot(harvest.fig %>% filter(count=="Harvest rate")) + 
  geom_ribbon(aes(x = year, ymin = low95, ymax = hi95, col = count, fill = count), alpha=0.5) +
  geom_line(aes(x = year, y = med50, col = count), size = 1) + 
  ylab("Harvest rate (%)") +
  xlab("Year") +
  scale_color_manual(values=c('#999999'))+
  scale_fill_manual(values=c('#999999')) +
  scale_y_continuous(position = "right") +
  theme_bw() +
  theme(legend.position = "none",
        plot.margin = margin(40,20,0.5,0.5)) +
  facet_wrap(~stock, nrow=4)

counts.fig$stock <- factor(counts.fig$stock, levels = c("Canada", "Middle", "Lower", "Total"))

a <- ggplot(counts.fig) + 
  geom_ribbon(aes(x = year, ymin = low95, ymax = hi95, col = count, fill = count), alpha=0.5) +
  geom_line(aes(x = year, y = med50, col = count), size = 1) + 
  ylab("Fish (000s)") +
  xlab("Year") +
  scale_color_manual(values=c('#999999','#E69F00')) +
  scale_fill_manual(values=c('#999999', '#E69F00')) +
  theme_bw() +
  theme(legend.position = "top",
        legend.title = element_blank(),
        plot.margin = margin(0.5,20,0.5,0.5)) +
  facet_wrap(~stock, nrow=4, scales = "free_y")

g <- ggarrange(a,b, 
               ncol = 2, 
               labels = c("a", "b"),
               widths = c(1, 1),
               label.y = c(0.935,0.935),
               label.x = c(0,-0.08))

print(g)
```

**Figure 1**. Reconstructed (a) harvest rates and (b) total run size and spawning escapements of Yukon River Chinook salmon by stock and combined. Thick lines are medians and shaded areas indicate 95% credible intervals.

## CDN-origin spawner-recruitment relationship

```{r fig2, echo=FALSE, fig.align = "center", fig.dim = c(7, 3), results='hide'}
spwn <- exp(model_bodies_pars$lnS)
spwn.quant <- apply(spwn, 2, quantile, probs=c(0.05,0.5,0.95))[,1:(length(sr_years)-4)]

rec <-exp(model_bodies_pars$lnR)
rec.quant <- apply(rec, 2, quantile, probs=c(0.05,0.5,0.95))[,8:dim(model_bodies_pars$R)[2]]

rps <- rec[,8:dim(model_bodies_pars$R)[2]]/spwn[,1:(length(sr_years)-4)]
rps.quant <- apply(rps, 2, quantile, probs=c(0.025,0.5,0.975))

brood_t <- as.data.frame(cbind(sr_years[1:(length(sr_years)-4)],t(spwn.quant), t(rec.quant), t(rps.quant)))
colnames(brood_t) <- c("BroodYear","S_lwr","S_med","S_upr","R_lwr","R_med","R_upr","RpS_lwr","RpS_med","RpS_upr")


# SR relationship
spw <- seq(0,max(brood_t[,4]),length.out=100)
SR_pred <- matrix(NA,100,max_samples)
SR_early <- matrix(NA,100,max_samples)
SR_late <- matrix(NA,100,max_samples)

for(i in 1:max_samples){
  r <- sample(seq(1,max_samples),1,replace=T)
  a <- model_bodies_pars$lnalpha_c[r]
  a_t <- model_bodies_pars$lnalpha_y[r,c(8:(dim(model_bodies_pars$lnalpha_y)[2]-4))]
  b <- model_bodies_pars$beta[r]
  
  SR_pred[,i] <- (exp(a)*spw*exp(-b*spw))
  SR_early[,i] <- (exp(median(a_t[1:11]))*spw*exp(-b*spw))
  SR_late[,i] <- (exp(median(a_t[23:33]))*spw*exp(-b*spw))
}

SR_pred <- cbind(spw,t(apply(SR_pred,c(1),quantile,probs=c(0.10,0.5,0.9),na.rm=T)))
colnames(SR_pred) <- c("Spawn", "Rec_lwr","Rec_med","Rec_upr")
SR_pred <- as.data.frame(SR_pred)

a <- ggplot() +
  geom_ribbon(data = SR_pred, aes(x = Spawn, ymin = Rec_lwr, ymax = Rec_upr),
              fill = "grey80", alpha=0.5, linetype=2, colour="gray46") +
  geom_line(data = SR_pred, aes(x = Spawn, y = Rec_med), color="black", size = 1) +
  geom_errorbar(data = brood_t, aes(x= S_med, y = R_med, ymin = R_lwr, ymax = R_upr),
                colour="grey", width=0, size=0.3) +
  geom_errorbarh(data = brood_t, aes(x= S_med, y = R_med, xmin = S_lwr, xmax = S_upr),
                 height=0, colour = "grey", height = 0, size = 0.3) +
  geom_point(data = brood_t, aes(x = S_med, y = R_med, color=BroodYear, width = 0.9), size = 3)+
  coord_cartesian(xlim=c(0, 130000), ylim=c(0,max(brood_t[,7]))) +
  scale_colour_viridis_c()+
  xlab("Spawners") +
  ylab("Recruits") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.key.size = unit(0.4, "cm"),
        legend.title = element_text(size=9),
        legend.text = element_text(size=8))+
  geom_abline(intercept = 0, slope = 1,col="dark grey")


# plot estimate of time varying productivity
lnRS<- log(brood_t$R_med/brood_t$S_med)
brood_t_lnRS  <- cbind(brood_t,lnRS); colnames(brood_t_lnRS)[3] <- "S"; colnames(brood_t_lnRS)[1] <- "BY" # add log(R/S) to brood table and change spawners column name to S for Kalman filter function

source(here("02_models/Kalman_code.R"))

kalman_fit <- run.kalman.Ricker(brood_t_lnRS[1:35,]) # only estimate time varying productivity for complete brood years

b <- ggplot(kalman_fit$df, aes(x=BY, y = exp(a.smooth) ), show.legend = F) +
  geom_line(show.legend = F, color = rgb(1,0,0, alpha=0.2), lwd = 1.5) + 
  geom_ribbon(aes(ymin = exp(a.smooth-(a.smooth.var*6)), ymax = exp(a.smooth+(a.smooth.var*6))), show.legend = F, fill = rgb(1,0,0, alpha=0.2)) +
  xlab("Brood year") +
  ylab("Intrinsic productivity") +
  theme(legend.position = "none") +
  geom_abline(intercept = 1, slope = 0 ,col="dark grey", lty=2) +
  theme_bw()+
  coord_cartesian(ylim=c(0,10)) 

g <- ggarrange(a,b,nrow =1,  widths = c(1,0.65), labels="auto")

print(g)
```

**Figure 2**. Spawner-recruitment relationship and productivity over time.(a) Relationship between recruitment and spawner abundance for Canadian-origin Yukon Chinook salmon from 1982 to 2022. Error bars and grey band are 95% credible intervals, thick black line is the expected relationship. (b) Estimated time-varying intrinsic productivity for brood years with complete returns. Note estimate of time varying productivity is generated post model fit by fitting a linear Ricker model with random walk on alpha parameter using methods details in [Peterman et al.  2000](https://cdnsciencepub.com/doi/abs/10.1139/f99-204).

## Probability profiles

```{r fig3, echo=FALSE, fig.align = "center", fig.height=7}
spw <- seq(0,max(brood_t[,4]),length.out=100)

Profiles <- array(NA, dim = c(length(spw),max_samples,9))

for(i in 1:max_samples){
  r <- sample(seq(1,max_samples),1,replace=T)
  a <- model_bodies_pars$lnalpha_c[r]
  b <- model_bodies_pars$beta[r]
  S_msy_c <- model_bodies_pars$Smsy_Sch_corr[r]
  R_msy_c <- S_msy_c*exp(a-b*S_msy_c)
  msy_c <- R_msy_c - S_msy_c
  U_max_c <- 1-(1/exp(a))
  Umsy_Sch_corr <- model_bodies_pars$Umsy_Sch_corr[r]

  for(j in 1:length(spw)){
    spw_star <- spw[j]
    R_star <- spw_star*exp(a-b*spw_star)
    sus_yield <- R_star - spw_star
    U <- ifelse(sus_yield/R_star < 0, 1, sus_yield/R_star)
    Profiles[j,i,1] <- ifelse(sus_yield > 0.9*msy_c, 1, 0) # probability yield > 90% of MSY
    Profiles[j,i,2] <- ifelse(sus_yield > 0.8*msy_c, 1, 0) # probability yield > 80% of MSY
    Profiles[j,i,3] <- ifelse(sus_yield > 0.7*msy_c, 1, 0) # probability yield > 70% of MSY
    Profiles[j,i,4] <- ifelse(R_star > 0.9*R_msy_c, 1, 0) # probability recruitment > 90% of MSR
    Profiles[j,i,5] <- ifelse(R_star > 0.8*R_msy_c, 1, 0) # probability recruitment > 80% of MSR
    Profiles[j,i,6] <- ifelse(R_star > 0.7*R_msy_c, 1, 0) # probability recruitment > 70% of MSR
    if(sus_yield < (0.9*msy_c) & spw_star < S_msy_c){
      Profiles[j,i,7] <- 1
    } else {
      Profiles[j,i,7] <- 0
      }
    if(sus_yield < (0.8*msy_c) & spw_star < S_msy_c){
      Profiles[j,i,8] <- 1
    } else {
      Profiles[j,i,8] <- 0
      }
    if(sus_yield < (0.7*msy_c) & spw_star < S_msy_c){
      Profiles[j,i,9] <- 1
    } else {
      Profiles[j,i,9] <- 0
      }    
        }
}

profiles_median <- cbind(spw,apply(Profiles,c(1,3),mean, na.rm=T))

colnames(profiles_median) <- c("Spawners","90% MSY","80% MSY","70% MSY", "90% MSR","80% MSR","70% MSR", "90% MSY ", "80% MSY ", "70% MSY ")
profiles_median <- as.data.frame(profiles_median)

long_yield_profiles <- profiles_median%>%
  select("Spawners","90% MSY","80% MSY","70% MSY")%>%
  pivot_longer(!Spawners, names_to = "Metric", values_to = "perc")

a <- ggplot(long_yield_profiles, aes(x = Spawners, y = perc, group = Metric, color = Metric)) +
      geom_line(size = 1.5) +
      scale_color_viridis(discrete = TRUE) +
      ylab("Probability") +
      theme(legend.position = "none") +
      theme_bw() +
      theme(axis.title.x = element_blank(),
      axis.text.x = element_blank(),
      legend.title = element_blank()) + 
  geom_rug(data = brood_t,
           aes(x = S_med),
           inherit.aes = FALSE,
           sides="b")

long_rec_profiles <- profiles_median%>%
  select("Spawners","90% MSR","80% MSR","70% MSR")%>%
  pivot_longer(!Spawners, names_to = "Metric", values_to = "perc")

b <- ggplot(long_rec_profiles, aes(x = Spawners, y = perc, group = Metric, color = Metric)) +
      geom_line(size = 1.5) +
      scale_color_viridis(discrete = TRUE) +
      ylab("Probability") +
      theme(legend.position = "none") +
      theme_bw() +
      theme(axis.title.x = element_blank(),
      axis.text.x = element_blank(),
      legend.title = element_blank()) + 
  geom_rug(data = brood_t,
           aes(x = S_med),
           inherit.aes = FALSE,
           sides="b")

long_overfish_profiles <- profiles_median%>%
  select("Spawners", "90% MSY ", "80% MSY ", "70% MSY ")%>%
  pivot_longer(!Spawners, names_to = "Objective", values_to = "perc")

c <- ggplot(long_overfish_profiles, aes(x = Spawners, y = perc, group = Objective, color = Objective)) +
  geom_line(size = 1.5) +
  scale_color_viridis(discrete = TRUE) +
  xlab("Spawners") +
  ylab("Probability ") +
  theme(legend.position = "none") +
  theme_bw() +
  theme(legend.title = element_blank()) + 
  geom_rug(data = brood_t,
           aes(x = S_med),
           inherit.aes = FALSE,
           sides="b")

g <- ggarrange(a,b,c,nrow =3, labels = c("a", "b", "c"), heights = c(0.75,0.75,0.9))
print(g)
```

**Figure 3**. Optimal probability profiles. (a) Optimal yield profile showing the probability that a given spawner abundance is expected to achieve 70%, 80%, or 90% of maximum sustainable yield (MSY). (b) Optimal recruitment profile showing the probability that a given spawner abundance is expected to achieve 70%, 80%, or 90% of maximum sustainable recruitment (S~MSR~). Historic spawning escapements are shown along x-axis. (c) Overfishing profile, calculated as 1 – P(SY > X% of MSY) at S < SMSY , and 0 at S > SMSY , showing the probability that sustained yield (SY) is reduced to less than a percentage (70%, 80%, or 90%) of MSY given a fixed level of escapement.



# Tables

## CDN run-reconstruction

**Table 1**. Reconstructed total run size, spawning escapements, harvest and harvest rates for the Canadian-origin Yukon River Chinook salmon stock. Shown are posterior medians. 

```{r}

cdn_RR_table <- round(cbind(sr_years, 
                  canrun.quant[,2]*1000,canesc.quant[,2]*1000,canhar.quant[,2],canharrate.quant[,2]))

colnames(cdn_RR_table) <-c("Year", "Total run", "Escapement", "Harvest", "Harvest rate (%)")

kable(cdn_RR_table,
      align = "crr") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```

## Lower Yukon River run-reconstruction

**Table 2**. Reconstructed total run size, spawning escapements, harvest and harvest rates for the lower Yukon River Chinook salmon stock. Shown are posterior medians. 

```{r}

lwr_RR_table <- round(cbind(sr_years, 
                      lowrun.quant[,2]*1000,lowesc.quant[,2]*1000,lowhar.quant[,2],lowharrate.quant[,2]))

colnames(lwr_RR_table) <-c("Year", "Total run", "Escapement", "Harvest", "Harvest rate (%)")

kable(lwr_RR_table,
      align = "crr") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```

## Middle Yukon River run-reconstruction

**Table 3**. Reconstructed total run size, spawning escapements, harvest and harvest rates for the middle Yukon River Chinook salmon stock. Shown are posterior medians. 

```{r}
mid_RR_table <- round(cbind(sr_years, 
                      midrun.quant[,2]*1000,midesc.quant[,2]*1000,midhar.quant[,2],midharrate.quant[,2]))

colnames(mid_RR_table) <-c("Year", "Total run", "Escapement", "Harvest", "Harvest rate (%)")

kable(mid_RR_table,
      align = "crr") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```

```{r}

RR_table <- rbind(
  cbind(rep("Canadian",times = dim(cdn_RR_table)[1]),cdn_RR_table),
  cbind(rep("Lower",times = dim(lwr_RR_table)[1]),lwr_RR_table),
  cbind(rep("Middle",times = dim(mid_RR_table)[1]),mid_RR_table)
  
)
colnames(RR_table) <-c("Stock", "Year", "Total run", "Escapement", "Harvest", "Harvest rate (%)")
write.csv(RR_table, here("03_outputs/rr-table-2022.csv"), row.names = FALSE)
```
## CDN spawner-recruitment parameters and reference points

**Table 4**. Posterior means, medians and credible intervals for leading spawner-recruitment parameters and associated biological benchmarks. Also show are estimates of the effective sample size and potential scale reduction factor for parameters and benchmarks estimated by the model.

```{r}
table.in <- benchmarks  %>% as.data.frame() %>%
            mutate(n_eff = prettyNum(round(n_eff),big.mark=",")) %>%
              rownames_to_column(var= "Variable") %>%
              dplyr::rename(Mean = mean,Median = "50%",p2.5 = "2.5%",p97.5 = "97.5%","n eff" = n_eff)

#table.in[9,2] <- 0.4265 # hard coded hack
table.in <- table.in[c(1:8,10),]

table.in$Variable <- c("log (alpha)", "beta","sigma R","phi","Smsr","Seq","Smsy","Umsy","Umsr") # BC: for some reason losing rownames in script above so adding them back in here

# formatting generally done by row or column inside kableExtra, but only by column (Var) in the source data frame
# this table has a mix of number types in each col and row.
# need to split, format, and stitch back together

right.cols <- table.in %>% select("n eff",Rhat) %>% mutate(Rhat = round(Rhat,4))

#right.cols <- right.cols[c(1:7,9,8,10),]

pars.chunk <- table.in %>% dplyr::filter(Variable %in% c("log (alpha)", "sigma R","phi")) %>%
                  select(Variable,Mean, Median, p2.5,p97.5) %>% 
                  mutate_at(2:5,function(x){ format(round(x,3), nsmall = 3)  }  ) %>%
                  mutate_at(2:5,function(x){as.character(x)}   )

beta.chunk <- table.in %>% dplyr::filter(Variable %in% c("beta")) %>%
                  select(Variable,Mean, Median, p2.5,p97.5) %>% 
                  mutate_at(2:5,function(x){ formatC(x,format="E",digits=3)  }  ) %>%
                  mutate_at(2:5,function(x){as.character(x)}   )  

pars.chunk <- bind_rows(pars.chunk,beta.chunk) 
pars.chunk <- pars.chunk[c(1,4,2,3),]

pars.chunk$Variable <- gsub("log \\(alpha\\)","logalpha",pars.chunk$Variable)
pars.chunk$Variable <- gsub("sigma R","sigmaR",pars.chunk$Variable)


bm.chunk <- table.in %>% dplyr::filter(Variable %in% c("Smsr","Seq","Smsy")) %>%
                  select(Variable,Mean, Median, p2.5,p97.5) %>% 
                     mutate_at(2:5,function(x){prettyNum(round(x),big.mark = ",")}   )


umsy.chunk <- table.in %>% dplyr::filter(Variable %in% c("Umsy","Umsr")) %>%
                  select(Variable,Mean, Median, p2.5,p97.5) %>% 
                     mutate_at(2:5,function(x){paste0(round(x*100),"%")}   )



table.in <- bind_rows(pars.chunk, bm.chunk,umsy.chunk) %>% bind_cols(right.cols) %>%
               mutate(Variable = recode(Variable,Smsy = "$S_{MSY}$",Seq = "$S_{EQ}$",
                      Umsy = "$U_{MSY}$",
                      Smsr = "$S_{MSR}$", beta = "$\\beta$", phi = "$\\phi$", sigmaR = "$\\sigma_R$",
                      Umsr = "$U_{MSR}$",logalpha = "$ln(\\alpha)$"))

names(table.in) <- gsub("n eff","$n_{eff}$",names(table.in))
names(table.in) <- gsub("Rhat","$\\\\hat{R}$",names(table.in))

table.in[is.na(table.in)] <-""
table.in[table.in == "NA"] <-"" # because prettyNum converts to character

kable(table.in,
      align = "crr") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))


```